### 2013-03-28 doc/sosp13/evaluation.tex

\paragraph{Putting it all together with Unbalanced Tree Search (UTS).} We now
show the overall performance of \Grappa running UTS.
Figure~\ref{fig:grappa-uts}. The point of this experiment is to show that
\Grappa's context switching and communication layers can in fact be used
together to run an irregular application efficiently. Looking at the
performance as the number of nodes grows shows \TODO{...}.

@@

\TODO{UTS: story here is T1 class is bushy trees similar to properties
    of real world networks. Larger T1XXL (4.5 B vertices) provides
    more parallelism for continued scaling up. T3 class is deep skinny
    trees. Grappa can do no better than the straightforward UPC impl: there very little
    parallelism and the critical path is long}

>>>>

\paragraph{Putting it all together with Unbalanced Tree Search in
    memory (UTS).}
We now show the overall performance of \Grappa running UTS.
Figure~\ref{fig:grappa-uts}. The point of this experiment is to
demonstrate whether \Grappa's context switching and communication layers can in fact
be used together, while balancing workload, to run an irregular application efficiently. 
We look at two classes of trees, T1x and T3x, from the
original benchmark. T1x trees are very shallow and wide, while T3x
trees are very deep. When the access to each vertex is a random
access, the critical path to search T3x trees is very long. On such
trees, we do not expect there to be sufficient concurrency for any
system, including \Grappa, to achieve high throughput. \TODO{plot it
    if time}. To verify this, at the 16-node data point, the average active tasks per
core over the search is 775 and 13 for T1XL and T3L, respectively.

@@

### 2013-03-28 doc/sosp13/intro.tex

Our evaluation of \Grappa shows that its core components provide scalable performance.  It can multiplex thousands of workers on a multicore CPU and is limited only by DRAM bandwidth, not latency, to fetch worker state.  The communication layer provides over 10X the small-message performance compared to the raw underlying message injection rate.  Combining these two components, \Grappa achieves 1.2 GUPS with 64 system nodes, far above any reported cluster performance~\cite{gups} for comprable systems.  When we compare \Grappa to native MPI implementations of more complex application kernels, the story is more muddled.  When the MPI implementation is carefully tuned to aggregate messages inside the application -- essentially duplicating the work \Grappa is doing for the programmer, without the generality and context switch overhead -- then the MPI implementation is between 4-10X faster.  We see this in our comparisons for breadth first search and integer sorting.  On the other hand, if the MPI version is implemented in a straightforward manner, as we see with PageRank, GUPS, and unbalanced tree search, \Grappa is 2-5X faster.  When we compare \Grappa to the custom Cray XMT, we find Grappa to be between 2X faster and 4X slower depending on the benchmark.  Overall we find this encouraging because \Grappa is scalable and achieves this performance from a mass-market cluster, hence adding more system nodes an inexpensive and attractive option.

>>>>

Our evaluation of \Grappa shows that its core components provide scalable performance.  It can multiplex thousands of workers on a multicore CPU and is limited only by DRAM bandwidth, not latency, to fetch worker state.  The communication layer provides over 10X the small-message performance compared to the raw underlying message injection rate.  Combining these two components, \Grappa achieves 1.3 GUPS with 64 system nodes, far above any reported cluster performance~\cite{gups} for comprable systems.  When we compare \Grappa to native MPI implementations of more complex application kernels, the story is more muddled.  When the MPI implementation is carefully tuned to aggregate messages inside the application -- essentially duplicating the work \Grappa is doing for the programmer, without the generality and context switch overhead -- then the MPI implementation is between 4-10X faster.  We see this in our comparisons for breadth first search and integer sorting.  On the other hand, if the MPI version is implemented in a straightforward manner, as we see with PageRank, GUPS, and unbalanced tree search, \Grappa is 2-5X faster.  When we compare \Grappa to the custom Cray XMT, we find \Grappa to be between 2X faster and 4X slower depending on the benchmark.  Overall we find this encouraging because \Grappa is scalable and achieves this performance from a mass-market cluster, hence adding more system nodes an inexpensive and attractive option.
